### 2013-03-30 exam6/1.tex
start on exam

\emph{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{6cm}
\rule{1cm}{0pt}\begin{tabular}{|c|l|@{/}r|}
\hline
{\bf Problem} & Points & out of \\ \hline
1 & & 19\\ \hline
2 & & 10\\ \hline
Extra & & 5 \\ \hline
{\bf Total} & & 28+5 \\ \hline
%{\bf Base}  & \multicolumn{2}{l|}{{\bf 56}} \\ \hline
\end{tabular}
\end{minipage}

@@

\begin{problem} \pts{??}

@@

\begin{enumerate}
\item Design an object-based data representation for JSON, Jr.
\newpage
\item Design a method for counting the number of strings in a JSON,
  Jr.~object.
\newpage
\item Among the 2M lines of code your employer maintains are 30,000
  lines of code devoted to implementations of the {\tt
    StringPred} interface, which is:
\begin{verbatim}
;; A StringPred implements
;; - apply : String -> Boolean
\end{verbatim}
These objects represent predicates on strings.  Now that your JSON,
Jr. library is in place, they've decided to put their predicates to
use in searching a large corpus of JSON data.  To accomodate this,
design the following method for JSON, Jr.~objects:
\begin{verbatim}
;; Find the first string in this JSON Jr object satisfying
;; given predicate, or #f if there's no such string.
;; find : StringPred -> String or #f
\end{verbatim}
\end{enumerate}

\end{problem}

\newpage
\ifrubric\else
[Here is some more space for the previous problem.]
\newpage
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem} \pts{19}

>>>>

\emph{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{6cm}
\rule{1cm}{0pt}\begin{tabular}{|c|l|@{/}r|}
\hline
{\bf Problem} & Points & out of \\ \hline
1 & & 20\\ \hline
2 & & 19\\ \hline
Extra & & 5 \\ \hline
{\bf Total} & & 39+5 \\ \hline
%{\bf Base}  & \multicolumn{2}{l|}{{\bf 56}} \\ \hline
\end{tabular}
\end{minipage}

@@

\begin{problem} \pts{20}

@@

\begin{enumerate}
\item Design an object-based data representation for JSON, Jr.

\ifrubric
\begin{alltt}
;; A JSON is one of:  [5pt]
;; - (new s% String)
;; - Array
;;
;; An Array is one of
;; - (new a0%)
;; - (new a+% JSON Array)

(define-class s%
  (fields val))

(define-class a0%)

(define-class a+%
  (fields hd tl))
\end{alltt}
\else
\newpage
[Here is some more space for the previous problem.]
\fi
\newpage

\item Design a method for counting the number of strings in a JSON,
  Jr.~object.
\ifrubric
\begin{alltt}
;; JSON implements [1pts]
;; - Count the number of strings in this object
;;   count-strings : -> Natural

;; in s% [1pt]
(define (count-strings) 1)

;; in a0% [1pt]
(define (count-strings) 0)

;; in a+% [1pt]
(define (count-strings)
  (+ (this . hd . count-strings)
     (this . tl . count-strings)))

;; [1pts]
(define eg1 (new s% "This is JSON"))
(define eg2 (new a+% eg1 (new a+% (new s% "Jr.") (new a0%))))
(define eg3 (new a+% (new a0%)
                 (new a+% (new a+% (new s% "So")
                               (new a+% (new s% "is") (new a0%)))
                      (new a+% (new s% "this")
                           (new a0%)))))

;; [1pts]
(check-expect (eg1 . count-strings) 1)
(check-expect (eg2 . count-strings) 2)
(check-expect (eg3 . count-strings) 3)
\end{alltt}
\else
\fi
\newpage
\item Among the 2M lines of code your employer maintains are 30,000
  lines of code devoted to implementations of the {\tt
    StringPred} interface, which is:
\begin{verbatim}
;; A StringPred implements
;; - apply : String -> Boolean
\end{verbatim}
These objects represent predicates on strings.  Now that your JSON,
Jr. library is in place, they've decided to put their predicates to
use in searching a large corpus of JSON data.  To accomodate this,
design the following method for JSON, Jr.~objects:
\begin{verbatim}
;; Find the first string in this JSON Jr object satisfying
;; given predicate, or #f if there's no such string.
;; find : StringPred -> String or #f
\end{verbatim}
\ifrubric
\begin{alltt}
;; in s%  [2pts]
(define (find p)
  (if (p . apply (this . val))
      (this . val)
      #f))

;; in a0% [1pts]
(define (find p) false)

;; in a+% [3pts]
(define (find p)
  (local [(define r (this . hd . find p))]
    (if (false? r)
        (this . tl . find p)
        r)))

;; [2pts]
;; A (new eq% String) implements StringPred
(define-class eq%
  (fields x)
  (define (apply y)
    (string=? (this . x) y)))

;; [1pts]
(check-expect (eg1 . find (new eq% "This is JSON")) "This is JSON")
(check-expect (eg1 . find (new eq% "this")) false)
(check-expect (eg2 . find (new eq% "This is JSON")) "This is JSON")
(check-expect (eg2 . find (new eq% "this")) false)
(check-expect (eg3 . find (new eq% "This is JSON")) false)
(check-expect (eg3 . find (new eq% "this")) "this")
\end{alltt}
\else
\fi
\end{enumerate}
\end{problem}

\ifrubric
\else
\newpage
[Here is some more space for the previous problem.]
\fi
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem} \pts{19}
